Add Plant Functional Type (PFT) labels

### 2021-04-27 R/add_plant_functional_type.Rmd
added PFt labels to cleaned spectra

```{r}

@@

The USDA maintains a database of plant information, some of it trait data, some of it life history. Check it out at http://plants.usda.gov/java/

>>>>

```{r add_pft_labels}
# select the columns to merge with all the spectra
pft_labels <- taxon_pft_lookup %>% 
  select(genusSpecies, commonName, pft_MRA, pft_MODIS, phenology, leafType, growthForm)

# join the PFT labels into the spectral data frame
cleaned_spectra_pft <- right_join(cleaned_spectra, pft_labels, by = "genusSpecies")

# write to a csv
write_csv(x = cleaned_spectra_pft,
          file = here::here("analysis", "data","derived_data", "cleaned_spectra_pft.csv"))
```

@@

The USDA maintains a database of plant information, some of it trait data, some of it life history: http://plants.usda.gov/java/
